Target Markdown

### 2022-11-22 _targets.Rmd
problem with function all_authors when run via targets: when the output of the function is zero (which in some cases is), targets signposts error saying "replacement has 1 row, data has 0"

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path),
              format = "qs"),
     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path), format = "qs"),
     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
     #          format = "qs"),
      tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(ids_complete, create_ids_complete(ids, db_path),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete))

@@

     # tar_target(matching, match(db_path, ids, gender),
     #            format = "qs"),
     # tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
     # tar_target(sup_control, read.csv2(sup_path),
     #          format = "qs"),
     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
     #          format = "qs"),
     # tar_target(final_data, refine_data(matching, db_path, ids, sup_control),
     #            format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     # tar_target(ids_full_vector,
     #           make_ids_full_vector(matching)),
    #  tar_target(all_pubs,
    #        get_all_pubs(db_path, matching, ids_complete), 
    #           format = "qs"),
    # tar_target(all_authors,
    #        read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
    #           format = "qs")

@@

```{targets article}
list(
    tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
)

>>>>

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
     #          format = "qs"),
      tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(ids_complete, create_ids_complete(ids, db_path)),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete))

@@

      tar_target(matching, match(db_path, ids, gender)),
      tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
     #          format = "qs"),
      tar_target(final_data, refine_data(matching, db_path, ids, sup_control)),

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
    #  tar_target(all_pubs,
    #        get_all_pubs(db_path, matching, ids_complete), 
    #           format = "qs"),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector))

@@

```{targets article}
list(
    # tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
)
